---
title: "MMM-With-Carryover-And-Saturation"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{MMM-With-Carryover-And-Saturation}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
  %\VignetteDepends{tidymodels}
  %\VignetteDepends{tidyverse}
  %\VignetteDepends{ggsci}
  %\VignetteDepends{broom.mixed}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  warning = FALSE,
  message = FALSE,
  fig.width = 8
)
```

# Packages

```{r setup}
library(tidymodels)
library(tidymmm)
data(mmm_imps)
data(mmm_spend)
```

## Additional Packages

```{r}
# library(tidyverse)
# library(ggsci)
# library(broom.mixed)
```

# Data

Impressions Data
```{r}
head(mmm_imps)
```
Spend Data
```{r}
head(mmm_spend)
```

# Model Recipes

Recipe without transformation
```{r}
ln_init_mmm <-
  recipe(kpi_sales ~ ., data = mmm_imps) |>
  add_role(c(mi_tv, mi_radio, mi_banners), new_role = "mi") |>
  update_role(Date, new_role = "temp") |>
  update_role_requirements("temp", bake = FALSE)
```

Recipe with transformations with default hyperparameters
```{r}
cs_init_mmm <-
  recipe(kpi_sales ~ ., data = mmm_imps) |>
  add_role(c(mi_tv, mi_radio, mi_banners), new_role = "mi") |>
  update_role(Date, new_role = "temp") |>
  update_role_requirements("temp", bake = FALSE) |>
  step_geometric_adstock(c(mi_banners, mi_tv, mi_radio)) |>
  step_hill_saturation(mi_banners, max_ref = TRUE) |>
  step_hill_saturation(mi_tv, max_ref = TRUE) |>
  step_hill_saturation(mi_radio, max_ref = TRUE)
```

Recipe with tuned carryover and saturation transformations
```{r}
cs_tuned_mmm <-
  recipe(kpi_sales ~ ., data = mmm_imps) |>
  add_role(c(mi_tv, mi_radio, mi_banners), new_role = "mi") |>
  update_role(Date, new_role = "temp") |>
  update_role_requirements("temp", bake = FALSE) |>
  step_geometric_adstock(mi_banners, decay = 0.226, max_carryover = 1) |>
  step_hill_saturation(mi_banners, shape =  1.97, max_ref = TRUE) |>
  step_geometric_adstock(mi_tv, decay = 0.233, max_carryover = 1) |>
  step_hill_saturation(mi_tv, shape = 0.799, max_ref = TRUE) |>
  step_geometric_adstock(mi_radio, decay = 0.382, max_carryover = 1) |>
  step_hill_saturation(mi_radio, shape = 1.33, max_ref = TRUE)
```

# Setup Workflows

Using the same linear regression with the Bayesian estimation engine `stan` from `rstanarm` package.

```{r}
lm_mod <- linear_reg() |> set_engine("stan")

ln_init_wflow <-
  workflow() |>
  add_model(lm_mod) |>
  add_recipe(ln_init_mmm)

cs_init_wflow <-
  workflow() |>
  add_model(lm_mod) |>
  add_recipe(cs_init_mmm)

cs_tuned_wflow <-
  workflow() |>
  add_model(lm_mod) |>
  add_recipe(cs_tuned_mmm)
```


# Fitting Models / Running Workflows

```{r}
# ln_init_fit <- ln_init_wflow |> fit(data = mmm_imps)
# cs_init_fit <- cs_init_wflow |> fit(data = mmm_imps)
# cs_tuned_fit <- cs_tuned_wflow |> fit(data = mmm_imps)
```

## Use `tidy` to extract fitted parameters

```{r}
# tidy(ln_init_fit, conf.int = TRUE)
# tidy(cs_init_fit, conf.int = TRUE)
# tidy(cs_tuned_fit, conf.int = TRUE)
```

# Post-Modeling

Named List of trained models
```{r}
# models <- list(
#   ln_init_fit = ln_init_fit,
#   cs_init_fit = cs_init_fit,
#   cs_tuned_fit = cs_tuned_fit
#   )
```

## Model Decomposition
```{r, message=FALSE, warning=FALSE}
# model_decomps <- decompose(models, new_data = mmm_imps, spend_data = mmm_spend)
# model_decomps
```

## Model Metrics & Fit
```{r}
# model_metrics(model_decomps, new_data = mmm_imps)
```

```{r}
# plot_model_fit(model_decomps)
```


## Contributions

Contribution percent breakdown
```{r}
# plot_base_contribution(model_decomps)
# plot_channel_contribution(model_decomps)
```


Channel contrbution volume and ROIs
```{r}
# channel_metrics(model_decomps)
```

Plot ROIs
```{r}
# plot_roi(model_decomps)
```

# Response Curves

Generate reponse from model decomposition
```{r}
# response <- response_curves(model_decomps)
```

Visualize response curves
```{r}
# plot_response_curves(response)
```

Estimate mROI and ROI from the response curves
```{r}
# mroi(response)
```

