---
title: "MMM-With-Carryover-And-Saturation"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{MMM-With-Carryover-And-Saturation}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  warning = FALSE,
  message = FALSE,
  fig.width = 8
)
```

# Packages

```{r setup}
library(recipes)
library(workflows)
library(parsnip)
library(tibble)
library(broom.mixed)
library(ggsci)
library(rstanarm)

library(tidymmm)
data(mmm_imps)
data(mmm_spend)
```

# Data

Impressions Data
```{r}
glimpse(mmm_imps)
```
Spend Data
```{r}
glimpse(mmm_spend)
```

# Model Recipes

Recipe without transformation
```{r}
ln_init_mmm <-
  recipe(kpi_sales ~ ., data = mmm_imps) |>
  add_role(c(mi_tv, mi_radio, mi_banners), new_role = "mi") |>
  update_role(Date, new_role = "temp") |>
  update_role_requirements("temp", bake = FALSE)
```

Recipe with transformations with default hyperparameters
```{r}
cs_init_mmm <-
  recipe(kpi_sales ~ ., data = mmm_imps) |>
  add_role(c(mi_tv, mi_radio, mi_banners), new_role = "mi") |>
  update_role(Date, new_role = "temp") |>
  update_role_requirements("temp", bake = FALSE) |>
  step_geometric_adstock(mi_banners) |>
  step_geometric_adstock(mi_tv) |>
  step_geometric_adstock(mi_radio) |>
  step_hill_saturation(mi_banners, max_ref = TRUE) |>
  step_hill_saturation(mi_tv, max_ref = TRUE) |>
  step_hill_saturation(mi_radio, max_ref = TRUE)
```

Recipe with tuned carryover and saturation transformations
```{r}
cs_tuned_mmm <-
  recipe(kpi_sales ~ ., data = mmm_imps) |>
  add_role(c(mi_tv, mi_radio, mi_banners), new_role = "mi") |>
  update_role(Date, new_role = "temp") |>
  update_role_requirements("temp", bake = FALSE) |>
  step_geometric_adstock(mi_banners, decay = 0.432, max_carryover = 1) |> 
  step_hill_saturation(mi_banners, shape = 1.30, max_ref = TRUE) |> 
  step_geometric_adstock(mi_tv, decay = 0.0181, max_carryover = 8) |> 
  step_hill_saturation(mi_tv, shape = 0.783, max_ref = TRUE) |> 
  step_geometric_adstock(mi_radio, decay = 0.193, max_carryover = 1) |> 
  step_hill_saturation(mi_radio, shape = 1.06, max_ref = TRUE)
```

# Setup Workflows

Using the same linear regression with the Bayesian estimation engine.

```{r}
lm_mod <- linear_reg() |> set_engine("stan")

ln_init_wflow <-
  workflow() |>
  add_model(lm_mod) |>
  add_recipe(ln_init_mmm)

cs_init_wflow <-
  workflow() |>
  add_model(lm_mod) |>
  add_recipe(cs_init_mmm)

cs_tuned_wflow <-
  workflow() |>
  add_model(lm_mod) |>
  add_recipe(cs_tuned_mmm)
```


# Fitting Models / Running Workflows

```{r}
ln_init_fit <- ln_init_wflow |> fit(data = mmm_imps)
cs_init_fit <- cs_init_wflow |> fit(data = mmm_imps)
cs_tuned_fit <- cs_tuned_wflow |> fit(data = mmm_imps)
```

## Use `tidy` to extract fitted parameters

```{r}
tidy(ln_init_fit, conf.int = TRUE)
tidy(cs_init_fit, conf.int = TRUE)
tidy(cs_tuned_fit, conf.int = TRUE)
```

# Post-Modeling

Named List of trained models
```{r}
models <- list(
  ln_init_fit = ln_init_fit,
  cs_init_fit = cs_init_fit,
  cs_tuned_fit = cs_tuned_fit
  )
```

## Model Decomposition
```{r, message=FALSE, warning=FALSE}
model_decomps <- decompose(models, new_data = mmm_imps, spend_data = mmm_spend)
model_decomps
```

## Model Metrics & Fit
```{r}
model_metrics(model_decomps, new_data = mmm_imps)
```

```{r}
plot_model_fit(model_decomps)
```


## Contributions

Contribution percent breakdown
```{r}
plot_base_contribution(model_decomps)
plot_channel_contribution(model_decomps)
```


```{r}
model_decomps |> 
  filter(model == "cs_tuned_fit") |> 
  plot_channel_contribution_month(
    begin_date = "2021-04-01", 
    end_date = "2022-01-01"
    )
```


Channel contrbution volume and ROIs
```{r}
channel_metrics(model_decomps)
```

Plot ROIs
```{r}
plot_roi(model_decomps)
```

# Response Curves

Generate response from model decomposition
```{r}
response <- response_curves(model_decomps)
response
```

Visualize response curves
```{r}
plot_response_curves(response)
```

Estimate mROI and ROI from the response curves
```{r}
mroi(response)
```


